---
title: "Data Cleaning, Exploratory Data Analysis"
author: "Raymond Lesiyon, Jasmine, "
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---
```{r}
#install.packages('naniar')
#install.packages('DT')
```

Libraries
```{r}
library(tidyverse)
library(ggcorrplot)
library(GGally)
library(naniar)
library(DT)
```
Data
```{r}
diabetic_readmission_data <- read.csv("../data/diabetic_data_initial.csv")
data_size<- NROW(diabetic_readmission_data)
```

Show the data
```{r}
datatable(t(head((diabetic_readmission_data))))
```

### Data Cleaning

## Missing values: 

```{r}
diabetic_readmission_data <- diabetic_readmission_data %>% mutate(across(where(is.character), ~na_if(., "?")))
gg_miss_var(diabetic_readmission_data[, colSums(is.na(diabetic_readmission_data)) > 0] , show_pct=T) + 
  labs(x ="features", y = "Missing values in the dataset") + 
  theme_bw()
```


## Handling Missing Values: 

- Drop weight, medical_speciality, payer_code; the enitre column.
- Remove the rows of diag_3, diag_2, and diag_1
- Impute by KNN

### Data type-conversion
 This code maps the diagnosis values to the categories provides
```{r}
for (col in c('diag_1', 'diag_2', 'diag_3')) {
  diabetic_readmission_data <- diabetic_readmission_data %>% 
    mutate(new_col = case_when(
      .data[[col]] %in%  c(390:459, 785) ~ 'Circulatory',
      .data[[col]] %in%  c(460:519, 786) ~ 'Respiratory',
      .data[[col]] %in%  c(520:579, 787) ~ 'Digestive',
      .data[[col]] %in%  c(800:999) ~ 'Injury',
      .data[[col]] %in%  c(710:739) ~ 'Musculoskeletal',
      .data[[col]] %in%  c(580:629, 788) ~ 'Genitourinary',
      .data[[col]] %in%  c(1:249, 251:279,680:709, 780:782, 784, 790:799, 782) ~ 'Neoplasms',
       startsWith(.data[[col]], '250' ) ~'Diabetes',
      .default = as.character('Other'))
   ) %>% mutate(!!col := new_col) %>% select(-new_col)
}

diabetic_readmission_data$diag_1 <- as.factor(diabetic_readmission_data$diag_1)
diabetic_readmission_data$diag_2 <- as.factor(diabetic_readmission_data$diag_2)
diabetic_readmission_data$diag_3 <- as.factor(diabetic_readmission_data$diag_3)
```
### Changing categorical data to as factors;
```{r}
diabetic_readmission_data$encounter_id <- as.factor(diabetic_readmission_data$encounter_id)
diabetic_readmission_data$patient_nbr <- as.factor(diabetic_readmission_data$patient_nbr)

diabetic_readmission_data$race <- as.factor(diabetic_readmission_data$race)
diabetic_readmission_data$gender <- as.factor(diabetic_readmission_data$gender)
diabetic_readmission_data$age <- as.factor(diabetic_readmission_data$age)

diabetic_readmission_data$admission_type_id <- as.factor(diabetic_readmission_data$admission_type_id)
diabetic_readmission_data$discharge_disposition_id <- as.factor(diabetic_readmission_data$discharge_disposition_id)
diabetic_readmission_data$admission_source_id <- as.factor(diabetic_readmission_data$admission_source_id)
diabetic_readmission_data$medical_specialty <- as.factor(diabetic_readmission_data$medical_specialty)

for (i in c(23:NCOL(diabetic_readmission_data))) {
  diabetic_readmission_data[, i] <- as.factor(diabetic_readmission_data[, i])
}
```

## Removing dead or hospice patients; remove the repeated patients only (only keep the first encounter)
```{r}
dead_hospice <- c(11,13,14,19,20,21,18,25,26)
diabetic_readmission_data_iid <- diabetic_readmission_data %>%
  group_by(by =patient_nbr) %>%
  arrange(encounter_id) %>%
  slice(1) %>%
  filter(!discharge_disposition_id %in% dead_hospice)
```

## Convert the data into admitted or not admitted category

--> <30, >30 : 1
--> NO: 0

```{r}
diabetic_readmission_data_iid$y <- as.factor(ifelse(diabetic_readmission_data_iid$readmitted == '<30', 1, 0))
```

## Univariate distributions
### Distributions for each numerical feature in the dataset
```{r}
data<- diabetic_readmission_data_iid[, unlist(lapply(diabetic_readmission_data_iid, is.factor))]
col_names <- names(data)
nums_subplots <- 8
for (col_s in seq(1, NCOL(data), nums_subplots )) {
  long_data <- pivot_longer(data[, seq(col_s:min(col_s+8, 40))], col_names[seq(col_s:min(col_s+8, 40))],
               names_to="features",
               values_to="values")
  g <- ggplot(long_data, aes(x=values, fill=features)) + 
    geom_histogram(stat='count') + 
    facet_wrap(~ features, scales = "free") + 
    ggtitle("Categorical Features Distribution") + coord_flip() + 
    scale_y_continuous(breaks = scales::pretty_breaks(n=5)) +
    theme(legend.position = "top", strip.text.x = element_blank(),
                        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  print(g)
}

```

```{r}
data<- diabetic_readmission_data_iid[, unlist(lapply(diabetic_readmission_data_iid, is.numeric))]
col_names <- names(data)
nums_subplots <- 9
for (col_s in seq(1, NCOL(data), nums_subplots )) {
  long_data <- pivot_longer(
    data[, seq(col_s:min(col_s+nums_subplots, NCOL(data)))], 
    col_names[seq(col_s:min(col_s+nums_subplots, NCOL(data)))],
               names_to="features",
               values_to="values"
    )
  g <- ggplot(long_data, aes(x=values, fill=features)) +
    geom_histogram() + 
    facet_wrap(~ features, scales = "free") + 
    ggtitle("Numerical Features Distribution") + 
    scale_y_continuous(breaks = scales::pretty_breaks(n=5))
  print(g)
}
```



### Correlation for each class:

```{r}
col_names <- c("num_lab_procedures", "num_procedures", "time_in_hospital", "num_medications", "number_outpatient", "number_emergency", "number_inpatient", "number_diagnoses")
##class 0: 
numeric_data <- diabetic_readmission_data_iid %>%
  filter(y == 0)
ggcorrplot(cor(numeric_data[, col_names]))
```

```{r}
numeric_data <- diabetic_readmission_data_iid %>% filter(y == 1)
ggcorrplot(cor(numeric_data[col_names]))
```

```{r}
View(diabetic_readmission_data_iid)
```




References: 

1. http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2