---
title: "Project"
author: ""
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

Libraries
```{r}
library(tidyverse)
library(ggcorrplot)
library(GGally)
library(moments)
```
Data
```{r}
diabetic_readmission_data <- read.csv("../data/diabetic_data_initial.csv")
table(diabetic_readmission_data$readmitted)
#View(diabetic_readmission_data)
data_size<- NROW(diabetic_readmission_data)
## Removing dead or hospice patients

## convert diag values
diabetic_readmission_data<- convert_diags(diabetic_readmission_data)
```

```{r}
## Removing dead or hospice patients; remove the repeated patients only (only keep the first encounter)

dead_hospice <- c(11,13,14,19,20,21,18,25,26)
diabetic_readmission_data <- diabetic_readmission_data %>%
  group_by(by =patient_nbr) %>%
  arrange(encounter_id) %>%
  slice(1) %>%
  filter(!discharge_disposition_id %in% dead_hospice)
```

## Convert the data into admitted or not admitted category

--> <30, >30 : 1
--> NO: 0

```{r}
#diabetic_readmission_data$y <- as.factor(ifelse(diabetic_readmission_data$readmitted == '<30' | 
#         diabetic_readmission_data$readmitted == '>30', 1,0))
#table(diabetic_readmission_data$y)
```
### Correlation for each class:

```{r}
col_names <- c("num_lab_procedures", "num_procedures", "time_in_hospital", "num_medications", "number_outpatient", "number_emergency", "number_inpatient", "number_diagnoses")
#View(col_names)

##class 0: 
n_ <- diabetic_readmission_data %>% filter(y == 0)
ggcorrplot(cor(n_[col_names]))
```

```{r}
## Class 1
n_ <- diabetic_readmission_data %>% filter(y == 1)
ggcorrplot(cor(n_[col_names]))
```

```{r}
col_names <- append(col_names,"y")
ggpairs(diabetic_readmission_data, columns=col_names, aes(color = y, alpha = 0.5))
```

## Visualizing Categorical Variables
```{r}
str(diabetic_readmission_data)
```

```{r}
medicine1 <- c("metformin","repaglinide","nateglinide","chlorpropamide","glimepiride","acetohexamide","y")
medicine2 <- c("glipizide","glyburide","tolbutamide","pioglitazone","rosiglitazone","acarbose","y")
medicine3 <- c("miglitol","troglitazone","tolazamide","examide","citoglipton","insulin","y")
medicine4 <- c("glyburide.metformin","glipizide.metformin","glimepiride.pioglitazone","metformin.rosiglitazone","metformin.pioglitazone","y")
ggpairs(diabetic_readmission_data, columns=medicine1, aes(color = y, alpha = 0.5))
ggpairs(diabetic_readmission_data, columns=medicine2, aes(color = y, alpha = 0.5))
ggpairs(diabetic_readmission_data, columns=medicine3, aes(color = y, alpha = 0.5))
ggpairs(diabetic_readmission_data, columns=medicine4, aes(color = y, alpha = 0.5))

```
## Numerical Variables Transformations
#Removing weight, payer code, and medical speciality features because they are missing a lot of data
```{r}
#Removing weight, payer code, and medical specialty features
new_diabetic_readmission_data <- subset(diabetic_readmission_data, select = -c(weight, payer_code, medical_specialty))
#new_diabetic_readmission_data #verifying those columns are gone

#code checking/removing missing values from diagnoses 3. I commented it out for now because I would like to discuss this with the group. 
#checking out many missing values are in diag_3 column 
sum(grepl("\\?", diabetic_readmission_data$diag_3))
sum(grepl("\\?", diabetic_readmission_data$diag_1))
sum(grepl("\\?", diabetic_readmission_data$diag_2))
length(diabetic_readmission_data$diag_3)

#1419 rows are missing from diag_3
#356 rows are missing from diag_2
#20 rows are missing from diag 1

#To remove the entire column: 
#new_diabetic_readmission_data <- subset(diabetic_readmission_data, select = -c(diag_3))

#To remove the rows:
new_diabetic_readmission_data <- new_diabetic_readmission_data[!grepl("\\?", new_diabetic_readmission_data$diag_3), ]
new_diabetic_readmission_data <- new_diabetic_readmission_data[!grepl("\\?", new_diabetic_readmission_data$diag_2), ]
new_diabetic_readmission_data <- new_diabetic_readmission_data[!grepl("\\?", new_diabetic_readmission_data$diag_1), ]
new_diabetic_readmission_data <- new_diabetic_readmission_data[!grepl("\\?", new_diabetic_readmission_data$race), ]
new_diabetic_readmission_data

#To remove race '?'
new_diabetic_readmission_data <- new_diabetic_readmission_data[!grepl("\\?", new_diabetic_readmission_data$race), ]
new_diabetic_readmission_data

sum(grepl("\\?", new_diabetic_readmission_data$diag_3))
sum(grepl("\\?", new_diabetic_readmission_data$diag_1))
sum(grepl("\\?", new_diabetic_readmission_data$diag_2))
sum(grepl("\\?", new_diabetic_readmission_data$race))
```
### Categorical Variables Transformations
```{r}
source('FeatureEngineering.R', local = knitr::knit_global())
```

#log transformation of numerical variables 
#Purpose: normalizing dataset. reduce knewness of a measurement variable.
```{r}
num_data <- select_if(new_diabetic_readmission_data, is.numeric)
#apply(num_data, 2, skewness)

diabetic_readmission_transformations <- new_diabetic_readmission_data %>%
  mutate(log_time_in_hospital = log(time_in_hospital),
         log_num_lab_procedures = log(num_lab_procedures),
         log_num_procedures = log(num_procedures + 1),
         log_num_medications = log(num_medications),
         log_num_outpatient = log(number_outpatient + 1),
         log_num_emergency = log(number_emergency + 1),
         log_num_inpatient = log(number_inpatient + 1),
         log_num_diagnoses = log(number_diagnoses))
diabetic_readmission_transformations
```
 
 
References: 

1. http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2